### 2022-11-08 NSF2022/Description/backgroundv2.tex
background, SA1

\noindent
{\bf Collaborative Research: Mathematical modeling and simulation of
self-assembling amphiphilic particles in solvent {\bf MAKE MORE MATHEMATICAL}} \\
{\em Rolf Ryham (PI, Fordham University),
Bryan Quaife (lead PI, Florida State University), and
Yuan-Nan Young (PI, New Jersey Institute of Technology)}

@@

\subsection{Problem formulation}
Recently, we have developed a new mathematical model of
self-organization~\cite{FuQuRyYo22,ru-ryh-qua-you2022,Fu2018_SIAM}. The
model takes ideas from the phase field method and leverages boundary
integral equations to speed up computations. To formulate the problem,
consider a collection of $N_b$-many rigid bodies $U_i$, with boundary
$\Gamma_i$, immersed in an incompressible, zero-Reynolds number fluid
$\Omega_t = \RR^n \setminus \cup_{i=1}^{N_b} U_i$. The subscript $t$
reinforces that $\Omega_t$ is time-varying. We use the grain shape and
boundary conditions to capture the local properties of the suspended
media. Unlike particles, the bodies, which we will call grains, have
finite size.  \todo[inline]{using `grains' as an easy find-replace for
when we settle on vocabulary}

The first key idea is to define the grain interactions using a boundary
value problem
\begin{alignat}{3}
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, \:
  \nabla \cdot \uu = 0, \quad &&\xx \in \Omega_t, \label {eqn:stokes} \\
  -\rho^2 \Delta \eta + f'(\eta) &= 0, &&\xx \in \Omega_t,
  \label{eqn:phase}
\end{alignat}
with boundary conditions
\begin{alignat}{3}
  \frac{d\xx}{dt} &= \uu, &&\xx \in \bd\Omega_t \label{eqn:noslip} \\
  \uu &= \vv_i + \omega_i \times (\xx - \aa_i), \quad &&\xx \in
  \Gamma_i,\, i=1,\ldots,N_b, \label{eqn:rbm} \\
  \eta &= h_i(\xx,t),  &&\xx \in \Gamma_i,\, i=1,\ldots,N_b,
  \label{eqn:material}
\end{alignat}
and
\begin{align}
\int_{\Gamma_i} \mu(\nabla \uu + \nabla \uu^T + pI)\nnu \,\dif s = 
\int_{\Gamma_i}
\underbrace{\left(-\rho^{-1} f'(\eta)
  + \rho\left(\tfrac{1}{2}|\nabla \eta|^2 - \nabla \eta \nabla
  \eta^T\right)\right)}_{T_i}
  \nnu \, \dif s,
  \label{eqn:stressbalance}
\end{align}
where $\nnu$ is the unit outward normal vector. This is a semi-linear
system for evolution of the grains.  Equation~\eqref{eqn:stokes} is the
Stokes equations that describes the velocity $\uu$ and pressure $p$ of
the viscous aqueous phase.  Equation~\eqref{eqn:phase} describes the
phase transitions of the scalar order parameter $\eta$ with a decay
length $\rho$. Mathematically, this order parameter is responsible for
the attraction and adhesion between grains that want to align boundaries
of like phase. Physically, water molecules are polar and $\eta$
describes the orientational order of water e.g.~$\eta = 1$ when water
molecules share alignment and $\eta = 0$ when the water orientations are
disordered. The well-potential $f$ accounts for possibly distinct
equilibrium phases, as occurs with 3-bond and 4-bond hydrogen bonding.

The next three equations are the moving domain boundary conditions.
Equations~\eqref{eqn:noslip} and~\eqref{eqn:rbm} specify a no-slip
boundary condition for a rigid body with translation velocity $\vv_i$
and angular velocity $\omega_i$ about the point $\aa_i \in \Omega_i$. In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the water phase at the water-grain interface. This material
label is transported by the fluid and therefore satisfies $h_i(\xx,t) =
h^0_i(\xx(\XX,t),t)$ where $h_i^0$ and $\XX$ are reference labels,
coordinates given by the initial conditions, and $\xx(\XX,t)$ is the
flow map for the rigid bodies. Finally,
equation~\eqref{eqn:stressbalance} closes the system by requiring that
the hydrodynamic stress is balanced by the water-order stress.

Intriguingly, the
formulation~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} captures
exactly the right behavior expected from amphiphilic self-assembly.
Three bodies with amphiphilic label spontaneously translate and change
orientations to sequester the disordered fluid phase. In our simulations
(see section ()), we include a finite length repulsion to avoid particle
collisions. Moreover, a simple change of boundary conditions from
amphiphilic, to biased hydrophobic, to polar results in distinct
equilibrium morphologies (Figure~\ref{fig:self-assembly2}).

\begin{figure}[h]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.8in}m{1.8in}m{1.8in}}            
      (a)
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B3.jpg}    \\
     (b)
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C3.jpg}    \\
    (c)
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A3.jpg}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{long time}
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Rows (a)-(c) have
  the same initial configuration but different boundary conditions $g$.
  In row (a), self-assembly with an amphiphilic boundary condition
  results in a bilayer pattern shielding the hydrophobic core (yellow,
  $u > 0$) from the aqueous phase (blue, $u = 0$). Row (b) shows
  particles with a hydrophobic intensity that is greater on one side of
  the particle (magenta) than the other (yellow). In row (c), green is
  for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$. Particles
  orient like sides to form a checkerboard pattern.}
\end{figure}

The system~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} has an elegant
mathematical structure. In terms of locally in time well-posedness,
given disjoint grains with sufficiently smooth boundaries and data, the
system always has a solution and these solutions have a locally
Lipschitz dependence on the particle centers and orientations.
Solutions of~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} obey the
energy law
\begin{align}
  F = \int_{\Omega_t}
  \left(\rho |\nabla \eta|^2 + \rho^{-1} f(\eta)\right) \,d\xx,
  \quad
  \frac{d}{dt}F
  = - \int_{\Omega_t} \left(\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2\right) \,d\xx.
\end{align}
Mathematically, this energy law states that the free energy $F$ of the
water order phase transitions, which depends on the grain
configurations, is lost due to hydrodynamic dissipation. It is evident
that minimizers of the functional $F$ are unique and satisfy the
Euler-Lagrange equation~\eqref{eqn:phase}. There is a subtlety in the
energy law, though. Namely, the time derivative of the free energy $F$
also involves the moving boundary, accounted for by the Rayleigh
Transport Theorem, and the fact that the boundary data for $\eta$ are
transported by the rigid body motion. In fact, the water order surface
stress $T_i$ is the variational derivative that shows up in this
calculation.

The model has a broad range of applicability to self-organization
phenomena in chemistry and biological physics. Since the formulation is
scale independent, it can represent a suspension of amphiphiles, where
the grains represent the mean properties of a small collection of
lipids, at the nanoscopic scale. For larger scales, the representation
is literal and the grains Janus spheres. The proposal deals with the
physical origins in section ().

To summarize, the
formulation~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} shares a lot
of the features in phase field modeling, with the big exception that the
free energy depends on the grain configurations, rather than phase field
function. To make an explicit connection though, we can consider a phase
field model where one ``fluid'' phase instantaneously reaches minimality
while the other ``solid'' phase moves to further decrease free energy.
The model is also closely related to a recent and strongly developing
direction studying colloids immersed in nematic liquid crystals. As is
the case for nematics, it is natural to understand what is the effect of
the flow in such a context, but a first step is to obtain some solid
well-posedness results. The proposal discusses some mathematical
generalizations in section ().

@@

A consequence of the dimension reduction in a BIE formulation is that
complex geometries are much easier to resolve than a mesh-based method
since only $\partial \Omega_t$ needs to be discretized
(Figure~\ref{fig:fem_vs_bie}). Additional advantages of a BIE
formulation includes a discretization that is high-order, or even
spectrally, accurate; results in a well-conditioned linear system that
can be solved iteratively with a mesh-independent number of iterations
of a Krylov method such as the generalized minimal residual method
(GMRES). However, BIEs do have several challenges: nearly touching
grains requires a quadrature rule for nearly-singular integrals; their
discretization results in dense matrices; and they cannot immediately be
applied to non-linear PDEs. The BIE community, including PI Quaife, has
developed a variety of tools to address these numerical challenges, and
we discuss our planned approach in Section~\ref{sec:specificaim2}.

%The boundary integral equation (BIE) method is the ideal numerical
%method for the present study in terms of computational cost and
%accuracy. Boundary integral equations require linear PDE and so we take
%$f(\eta) = \tfrac{1}{2}\eta^2$, yielding in () the so called screened
%Laplace equation $-\rho^2 \Delta \eta + \eta$. This is a Helmholtz
%equation with purely imaginary wave number, enabling us to represent the
%solution in terms of layer potentials:
%\begin{equation}
%  \eta(\xx) = \int_{\partial \Omega} \frac{\partial G}{\partial \nu}
%  \left(\frac{\xx-\yy}{\rho}\right) \sigma(\yy) \,ds_{\yy}
%\end{equation}
%where $\frac{\partial G}{\partial \nu}$ is the normal derivative of the
%fundamental solution of the screened Laplace equation
%(a Bessel function in two space dimensions and
%an exponential times the standard fundamental solution of the Laplace equation
%in three space dimensions).
%This representation allows us to transfer the boundary value problem ()-()
%to an equation only involving in terms of domain boundary.  
%
%The numerical advantages of doing so are as follows.  If $h = N^{-1}$ is
%the characeristic grid spacing of the grain boundaries, then a finite
%element or finite difference discretization of ()-() requires on the
%order of $N_b N^n$ grid points for dense suspensions.  In contrast BIE
%require onely With finite elements, mesh regeneration would be needed at
%each time step since the domain is moving.  In the boundary integral
%approach, collocation points can be selected for the initial grain
%configuration and then used throughout the time-course.  As a downside,
%integral equations require specialized quadrature routines to resolve
%self interactions and nearly touching grain boundaries.  Finally, the
%far field boundary conditions which are important for imposed flow
%problems automatically hold, whereas with finite element and finite
%difference methods artificial boundary conditions must be imposed.

\subsubsection{Problem formulation}
%\begin{wrapfigure}[h!]

The mathematical formulation is a nonlinear system for the dynamics of a
collection of particles. The interactions come from a system of 
partial differential equations (PDEs) that comprise hydrodynamic
interactions and hydrophobic interactions.
%The formulation prevents particle collisions through excluded volume
%potentials. 
The hydrodynamic interactions come from the mobility problem for rigid
particles immersed in a viscous solvent. We then use a
second-order Adams-Bashforth method to update the particle configuration.
Assuming inertial terms are
negligible, the particle motion is goverened by the Stokes equations
\begin{subequations}
  \label{eq:stokes}
  \begin{alignat}{3}
  \label{eq:stokes1}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
    \label{eq:stokes2}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokes3}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
  \end{alignat}
\end{subequations}
%\begin{alignat}{3}
%\label{eq:stokes1}
%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
%    && \xx \in \Omega, \\
%\label{eq:stokes2}
%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
%\label{eq:stokes3}
%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
%\end{alignat}
%
where $\uu$ is the velocity and $p$ is the pressure of the solvent,
$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
particles and changes shape as the particles move.
Since the particles are rigid, the solvent velocity satisfies
a no-slip boundary condition for a rigid body motion 
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
%\end{align}
on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
and angular velocity $\omega_i$ (Figure \ref{fig:flow_map}).
Given imposed forces acting on each
particle, the \emph{mobility problem} consists of finding
translational and angular velocities so that viscous fluid forces
balance the imposed forces.

The hydrophobic interactions come from the tendency of particles to
minimize the free energy of the structure of the surrounding water
molecules. The free energy functional takes the form 
\begin{equation}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{equation}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds
which is much smaller than characteristic time for 
particle motion \cite{MaGa13}.
Thus we assume $u$ minimizes $F[u]$ for all times.
Assuming appropriate conditions on $f(u)$ (\cite{evans10}, \S 8.2),
$u$ is bounded and satisfies the Euler-Lagrange equation
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
\text{ on } \bd\Omega.
\end{equation}
The boundary condition $g$ is a material label that is transported with
the particle (Figure~\ref{fig:bcs}).

The particles lower the free energy $F[u]$ of the surrounding water
by moving. We calculate the rate of change of $F[u]$ using
\emph{variation of the domain} ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
stress  
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
\end{align}
The imposed forces and torques come from the integration of $\mathbf{T}$
along the particle boundary.
These forces and torques couple the Stokes equations \eqref{eq:stokes},
to semilinear elliptic equation \eqref{eq:SL}.
Solving for the translational and rotational velocities gives the
particle evolution.

The stress~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions (Figure \ref{fig:3particles}).

%By solving the above system, we obtain translational and angular
%velocities of the many-body system. A second-order Adams-Bashforth
%scheme updates the particle positions and orientations.

The formulation presents a number of mathematical and numerical
challenges. For one, the domain is constantly changing so that a new
boundary value problem must be solved at each time step. The particle
boundaries are nearly touching and high-order numerical
schemes and adaptively chosen time-step sizes
are required to calculate trajectories accurately.
Furthermore, the domain is unbounded and care must be taken 
in capturing the far-field boundary conditions correctly. 
Finally, the numerical routine must handle large system sizes
efficiently.

%and
%\begin{equation}
%  \label{eq:force}
%  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i,\quad 
%  \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot (\ssigma \cdot \nnu) \,
%  \dif s = T_i, \qquad i=1,\ldots,N_b,
%\end{equation}
%where
%$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T \right)$
%is the hydrodynamic stress tensor (pressure tensor) and $\nnu$ is the
%particle outward normal.

>>>>

\noindent
{\bf Collaborative Research:
Collaborative research: self-orgzanization by moving domain elliptic PDE}\\
{\em Rolf Ryham (PI, Fordham University),
Bryan Quaife (lead PI, Florida State University), and
Yuan-Nan Young (PI, New Jersey Institute of Technology)}

@@

\subsection{Problem formulation}
Recently, we have developed a new mathematical model of
self-organization~\cite{FuQuRyYo22,ru-ryh-qua-you2022,Fu2018_SIAM}. The
model takes ideas from the phase field method and leverages boundary
integral equations to speed up computations. To formulate the problem,
consider a collection of $N_b$-many rigid bodies $U_i(t) \subset \mathbb{R}^n$
with boundary $\Gamma_i(t)$.
We call these bodies ``granules''.
The granules are immersed 
in an incompressible, zero-Reynolds number fluid
$\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b} U_i(t)$
(Figure \ref{fig:flow_map}).

We look for $N_b$-many rigid body transformations
\begin{equation}
\label{eq:RBT}
F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{equation}
where $i = 1,\ldots,N_b,$
$R_i(t)$ is a rotation (proper orthogonal) $n \times n$ matrix,
$\aa_i(t)$ are the granule centers, and $\XX$ is a reference coordinate.
The transformations \eqref{eq:RBT} tell us how the granules move through space
and we use the shape and
boundary conditions for $U_i$ to capture the local
properties of the suspended media e.g., lipids, peptides, Janus spheres.
Throughout, $\nu$ refers to unit normal pointing into $\Omega(t)$ (Figure \ref{fig:flow_map}).

The key idea is to define the dynamics using the following
boundary value problem system:
\begin{alignat}{4}
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  && \nabla \cdot \uu = 0, && \quad \xx \in \Omega(t), \label {eqn:stokes} \\
  \label{eqn:phase}
  -\rho^2 \Delta \eta + f'(\eta) &= 0, && &&\quad \xx \in \Omega(t),\\
\label{eqn:noslip}        
\uu(\xx) &= \frac{dF_i}{dt}(\XX,t)
&&=\vv_i + \omega_i \times (\xx - \aa_i), 
&&\quad \xx \in \Gamma_i(t),\\
\label{eqn:material}
\eta(\xx) &= h_i(\XX), &&  &&\quad \xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$
and where $\xx = F_i(\XX,t)$.
Finally,
\begin{equation}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left[\mu(\nabla \uu + \nabla \uu^T + pI) + T_i\right]\nnu \,\dif s = \mathbf{0},\quad
\end{equation}
where
\begin{equation}
\label{eqn:hydro_stress}
T_i = -\rho^{-1} f'(\eta)I
  + \rho\left(\tfrac{1}{2}|\nabla \eta|^2I - \nabla \eta \nabla
  \eta^T\right)
\end{equation}
for the identity matrix $I$.

The above form a semi-linear elliptic 
system for evolution of the granules.  Equation~\eqref{eqn:stokes} is the
Stokes equations that describes the velocity $\uu$ and pressure $p$ of
the viscous aqueous phase.  Equation~\eqref{eqn:phase} describes the
phase transitions of the scalar order parameter $\eta$ with a decay
length $\rho$. Mathematically, this order parameter is responsible for
the attraction and adhesion between granules that want to align boundaries
of like phase.

The next three equations are the moving domain boundary conditions.
Equations~\eqref{eqn:noslip} specify a no-slip
boundary condition for a rigid body with translation velocity $\aa'_i(t) = \vv_i$
and angular velocity $\omega_i$
about the point $\aa_i(t) \in U_i(t)$.
($\omega_i$ is the axial vector of the
skew symmetric matrix $R'_i(t)$.)
In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the phases at water-granule interface.
In other words, the boundary condition for $\eta$ is transported by the flow.
Finally,
equation~\eqref{eqn:stressbalance} closes the system by requiring that
the hydrodynamic stress is balanced by the phase stress $T_i$ in
\eqref{eqn:hydro_stress}.

We call the rigid bodies $U_i(t)$ granules since they are small, compact
parcels of a suspended medium, e.g. lipids, Janus spheres.
We have departed from the terminology ``particles'' here
to emphasize the role played by their finite size. 
In our simulations
(see section \ref{sec:specific_aim1}),
we include a finite length repulsion to avoid particle
collisions.

Intriguingly, the
formulation~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} captures
exactly the right behavior expected from amphiphilic self-assembly.
For example, three bodies with amphiphilic label
(see section \ref{sec:specific_aim1}) spontaneously
self-organize to sequester the hydrophobic fluid phase
(the red phase in Figure \ref{fig:flow_map}).
Moreover, a simple change of boundary conditions from
amphiphilic, to biased hydrophobic, to polar results in distinct
equilibrium morphologies (Figure~\ref{fig:self-assembly2}).

\begin{figure}[t!]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.8in}m{1.8in}m{1.8in}}            
      (a)
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B3.jpg}    \\
     (b)
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C3.jpg}    \\
    (c)
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A3.jpg}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{long time}
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize \label{fig:self-assembly2} Rows (a)-(c) have
  the same initial configuration but different boundary conditions $g$.
  In row (a), self-assembly with an amphiphilic boundary condition
  results in a bilayer pattern shielding the hydrophobic core (yellow,
  $u > 0$) from the aqueous phase (blue, $u = 0$). Row (b) shows
  particles with a hydrophobic intensity that is greater on one side of
  the particle (magenta) than the other (yellow). In row (c), green is
  for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$. Particles
  orient like sides to form a checkerboard pattern.}
\end{figure}

The system~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} has an elegant
mathematical structure. In terms of locally in time well-posedness,
given disjoint granules with sufficiently smooth boundaries and data, the
system always has a solution and these solutions have a locally
Lipschitz dependence on the particle centers and orientations.
Solutions of~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} obey the
energy law
\begin{align}
  F = \int_{\Omega_t}
  \left(\rho |\nabla \eta|^2 + \rho^{-1} f(\eta)\right) \,d\xx,
  \quad
  \frac{d}{dt}F
  = - \int_{\Omega_t} \left(\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2\right) \,d\xx.
\end{align}
Mathematically, this energy law states that the free energy $F$ of the
water order phase transitions, which depends on the granule
configurations, is lost due to hydrodynamic dissipation. It is evident
that minimizers of the functional $F$ are unique and satisfy the
Euler-Lagrange equation~\eqref{eqn:phase}. There is a subtlety in the
energy law, though. Namely, the time derivative of the free energy $F$
also involves the moving boundary, accounted for by the Rayleigh
Transport Theorem, and the fact that the boundary data for $\eta$ are
transported by the rigid body motion. In fact, the water order surface
stress $T_i$ is the variational derivative that shows up in this
calculation.

\begin{figure}[t!]
\begin{center}
\includegraphics[width=\textwidth]{figures/Background/coarsening.pdf}
\end{center}
\caption{\label{fig:coarsening}}
\end{figure}
The model has a broad range of applicability to self-organization
phenomena in chemistry and biological physics. Since the formulation is
scale independent, it can represent a suspension of amphiphiles, where
the granules represent the mean properties of a small collection of
lipids, at the nanoscopic scale. For larger scales, the representation
is literal and the granules Janus spheres. The proposal deals with the
physical origins in section ().

To summarize, the
formulation~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} shares a lot
of the features in phase field modeling, with the big exception that the
free energy depends on the granule configurations, rather than phase field
function. To make an explicit connection though, we can consider a phase
field model where one ``fluid'' phase instantaneously reaches minimality
while the other ``solid'' phase moves to further decrease free energy.
The model is also closely related to a recent and strongly developing
direction studying colloids immersed in nematic liquid crystals. As is
the case for nematics, it is natural to understand what is the effect of
the flow in such a context, but a first step is to obtain some solid
well-posedness results. The proposal discusses some mathematical
generalizations in section ().

@@

A consequence of the dimension reduction in a BIE formulation is that
complex geometries are much easier to resolve than a mesh-based method
since only $\partial \Omega_t$ needs to be discretized
(Figure~\ref{fig:fem_vs_bie}). Additional advantages of a BIE
formulation includes a discretization that is high-order, or even
spectrally, accurate; results in a well-conditioned linear system that
can be solved iteratively with a mesh-independent number of iterations
of a Krylov method such as the generalized minimal residual method
(GMRES). However, BIEs do have several challenges: nearly touching
granules requires a quadrature rule for nearly-singular integrals; their
discretization results in dense matrices; and they cannot immediately be
applied to non-linear PDEs. The BIE community, including PI Quaife, has
developed a variety of tools to address these numerical challenges, and
we discuss our planned approach in Section~\ref{sec:specificaim2}.
